---
title: "Individual Assignment"
description: |
  This post is built for Assignment of ISSS608 Visual Analytics and Application.
author:
  - name: LI Yuhong
    url: {}
date: 07-12-2021
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1. Overview
## 1.1 Background
This assignment topic is based on Mini-Challenge 3 of VAST Challenge 2021, and there is background introduction of VAST Challenge 2021.

In the roughly twenty years that Tethys-based GAStech has been operating a natural gas production site in the island country of Kronos, it has produced remarkable profits and developed strong relationships with the government of Kronos. However, GAStech has not been as successful in demonstrating environmental stewardship.

In January, 2014, the leaders of GAStech are celebrating their new-found fortune as a result of the initial public offering of their very successful company. In the midst of this celebration, several employees of GAStech go missing. An organization known as the Protectors of Kronos (POK) is suspected in the disappearance, but things may not be what they seem.

## 1.2 Data Used
The single data stream contains two major sources:

1. Microblog records that have been identified by automated filters as being potentially relevant to the ongoing incident.

2. Text transcripts of emergency dispatches by the Abila, Kronos local police and fire departments.

## 1.3 Objective

# 2. Literature Review
The literature review focus on the utilization of "Network" packages.

word cloud

line chart

network and relationship

# 3. Installation and load of R packages
* Packages "tidyverse", "tidyr", "tidyverse" and"dplyr" will be used to clean and wrangle data for final visualization.

* Packages "sp", "raster", "sf", "vctrs", "clock", "tmap", "rgdal", "readr" and "ggplot2" will be used for making visualization.

The code chunks below are used to install and load the packages in R.

```{r echo=TRUE}
packages = c("tidyverse","tidyr","tidyverse","dplyr","sp","raster","sf",
             "vctrs","clock","tmap","rgdal","readr","ggplot2")

for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

# 4. Data Preparation
## 4.1 Data Import and View
The data was imported by using read.csv().

```{r echo=TRUE}
cartrack <- read.csv("D:/SMU/Visual Analytics and Applications/Project and Assignment/Assignment/Challenge 2/MC2/car-assignments.csv")

creditcard <- read.csv("D:/SMU/Visual Analytics and Applications/Project and Assignment/Assignment/Challenge 2/MC2/cc_data.csv")

gps <- read.csv("D:/SMU/Visual Analytics and Applications/Project and Assignment/Assignment/Challenge 2/MC2/gps.csv")

loyaltycard <- read.csv("D:/SMU/Visual Analytics and Applications/Project and Assignment/Assignment/Challenge 2/MC2/loyalty_data.csv")
```

View the data by the following coding. 

```{r echo=TRUE}
view(cartrack)
view(creditcard)
view(gps)
view(loyaltycard)
```


The overview of data are shown in Table 1.

*Table 1*

S/N|Name of Data|Number of Observations|Variables
---|------------|----------------------|----------
1|cartrack|44|LastName, FirstName, CarID, CurrentEmploymentType, CurrentEmploymentTitle
2|creditcard|1490|timestamp, location, price, last4ccnum
3|gps|685,169|Timestamp, id, lat, long
4|loyaltycard|1392|timestamp, location, price, loyaltynum

## 4.2 Data Wrangling

## 4.3 Data Extraction

## 4.4 Final Data

# 5. Data Visualisation and Analysis
## 5.1 

# 6. Conclusion




